Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2016-12-19 paper/structureScene.tex
rephrase abstract

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
The emerging field of computational ecoacoustics aims at retrieving high-level information from the continuous, environmental recordings of acoustic sensors.
In this context, a central task is to cluster auditory scenes by similarity.
A convenient method considers bag-of-frames models and other representations based on summary statistics.
While these successfully characterize static scenes with little variability in sound content, they are unable to accurately differentiate scenes characterized by a few distinct sound events superimposed over a static background.
To address this problem, we propose a two-scale representation, which describes a signal at a short scale using scattering transforms while relying on a cluster model to characterize its larger-scale structure.
To motivate this, we validate the use of scattering transforms for supervised acoustic scene classification (ASC), illustrating its state-of-the-art performance compared to traditional features, such as mel-frequency cepstral coefficients (MFCCs).
Furthermore, we illustrate the power of the full cluster-based representation by applying it to an acoustic scene similarity retrieval (ASSR) task, where we again significantly outperform more traditional approaches based on summary statistics of MFCCs.

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
The emerging field of computational ecoacoustics aims at retrieving high-level information from the acoustic scenes recorded by some network of sensors.
In this context, a central task is to cluster acoustic scenes by similarity.
A convenient method considers bag-of-frames models and other representations based on summary statistics.
While these successfully characterize static scenes with little variability in sound content, they are unable to accurately differentiate scenes characterized by a few distinct sound events superimposed over a static background.
To address this problem, we propose a two-scale representation, which describes a signal at a short scale using scattering transforms while relying on a cluster model to characterize its larger-scale structure.
To motivate this, we validate the use of scattering transforms for supervised acoustic scene classification (ASC), illustrating its state-of-the-art performance compared to traditional features, such as mel-frequency cepstral coefficients (MFCCs).
Furthermore, we illustrate the power of the full cluster-based representation by applying it to an acoustic scene similarity retrieval (ASSR) task, where we again significantly outperform more traditional approaches based on summary statistics of MFCCs.
